---
title: "How many times have users turned off the notifications?"
output:
  pdf_document: default
  html_document: default
date: "05/06/2019"
---
```{r setup, include=FALSE}
# Options about chunks
knitr::opts_chunk$set(echo = FALSE, warning = FALSE, message = FALSE, tidy = TRUE)

# Reading final scores
library(xlsx)

# Loading Todyverse to work with tables
library(tidyverse)

# Printing table in a nice format
#library(kableExtra) #(This doesn't allow PDF creation)

```


## Step 1: Data selection

```{r Data selection}
# Collecting the ID of users
Uid_raw <- read.xlsx("data/UID.xlsx", header = TRUE, sheetIndex = 1)

# Collecting the list of UID
Uid_list <- read.xlsx("data/UID.xlsx", header = TRUE, sheetIndex = 2)%>%
  filter(Active=="Active")

# Counting the number of rows to check for errors  
r1<- nrow(Uid_raw)
r2<- nrow(Uid_list)
```

The selected file analyzes `r nrow(Uid_list)` users for `r nrow(Uid_raw)` days, from the beginning of the experimental phase (06.09.2017) until the end (11.01.2018).

## Step 2: Pre-processing

```{r Pre-processing}
### Pre-processing already done

head(Uid_raw)
```

Data has already been pre-processed and only data in the selected period and only notifications stating "The following UIDs have been unregistered" are shown.

## Step 3: Transformation

```{r Transformation of UID_Raw}
UID <- Uid_raw[,-2]%>%
  gather('UID01', 'UID02', 'UID03', 'UID04', 'UID05', 'UID06', 'UID07', 'UID08', 'UID09', 'UID10', 'UID11', 'UID12',
         key="Column", value="UID")%>% # Changing the shape of the table
  filter(UID!="NA")%>% # Removing UID associated to missing row in Users list tab
  arrange(Day)
```

For each day, the list of users is extracted.   

```{r}
head(UID) 
```

Each user appears once at the most every day.   
We check that by counting how many times a UID appears every day.  
```{r}
head(UID%>%
  group_by(Day)%>%
  count(UID))

```
Then, we filter only those that appear more than once. The resulting table is empty.
```{r}
UID%>%
  group_by(Day)%>%
  count(UID)%>%
  filter(n>1)
```

Some user in the list appears to be assigned to UID that are not in the user liste (UID= 64, 79,	108,	143,	162,	222,	237).
They shall be removed from the next table.   

```{r Transformation by adding condition}
Performance <- UID[,-2] %>%
  left_join(Uid_list,by="UID")%>% # Adding the list of users, to collect data about the type of intervention
  filter(Type!="NA") # Removing users that are not in the users list

head(Performance)
```

The resulting table allows obtaining the study conditions of each participant.

## Step 4: Data mining

The resulting table presents the sum of how many times participants have turned the system off, divided by type of intervention.   

```{r Data mining}
result <- Performance%>%
  group_by(Type)%>% # Gather results by type of intervention
  count(Type)

result

```

An in-depth analysis allows observing some interesting trends concerning how many times each user has turned the system off.   
```{r Data mining in depth}
# Listing the UID per type
result_details <- Performance%>%
  group_by(Type)%>%
  count(UID)

# Counting how many UID per type
UID_details <- result_details%>%
  group_by(Type)%>%
  count(Type)

# Assessing the average of events per Type
result_avg <- result
result_avg$n <- as.numeric(format(round(result$n/UID_details$n,2), nsmall = 2))
```

The amount of times each participant has turned the system off varies greatly among particiapants.  
```{r}
head(result_details,10)
```

By gathering the information about the participant, it is possible to count how many participants are listed in each type.   
```{r}
UID_details
```

Consequently, it is possible to obtain the average of how many times each user has turned the system off.   
```{r}
result_avg
```

In the end, it apperars that the average of `r result_avg$Type[1]` (`r result_avg$n[1]`) is smaller than the average of `r result_avg$Type[3]` (`r result_avg$n[3]`).

## Step 5: Evaluation

```{r Evaluation}
# NO additional test
```

As requested, the current analysis allows stating that:    

* In `r result$Type[1]` condition users turned off the notifications `r result$n[1]` amount of times.   
* In `r result$Type[2]` condition users turned off the notifications `r result$n[2]` amount of times.   
* In `r result$Type[3]` condition users turned off the notifications `r result$n[3]` amount of times.   
* In `r result$Type[4]` condition users turned off the notifications `r result$n[4]` amount of times.   

